NGO Repression as a Predictor of Worsening Human Rights Abuses

### 2021-11-12 manuscript/manuscript.Rmd
Add siunitx support

# R options
options(
  width = 90,  # Output width
  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
  knitr.kable.NA = "",  # Make NAs blank in kables
  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
  modelsummary_default = table_format  # Set modelsummary backend
)
```

>>>>

# R options
options(
  width = 90,  # Output width
  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
  knitr.kable.NA = "",  # Make NAs blank in kables
  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
  modelsummary_factory_default = table_format,  # Set modelsummary backend
)
}
```
